Ethereum: Un Registro Generico delle Transazioni Sicuro e Decentralizzato \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-02-02 Paper.tex
Update Paper.tex

\begin{enumerate}
\item The transaction is well-formed RLP, with no additional trailing bytes;
\item the transaction signature is valid;
\item the transaction nonce is valid (equivalent to the sender account's current nonce);
\item the gas limit is no smaller than the intrinsic gas, $g_0$, used by the transaction;
\item the sender account balance contains at least the cost, $v_0$, required in up-front payment.
\end{enumerate}

Formally, we consider the function $\Upsilon$, with $T$ being a transaction and $\boldsymbol{\sigma}$ the state:
\begin{equation}
\boldsymbol{\sigma}' = \Upsilon(\boldsymbol{\sigma}, T)
\end{equation}

Thus $\boldsymbol{\sigma}'$ is the post-transactional state. We also define $\Upsilon^g$ to evaluate to the amount of gas used in the execution of a transaction and $\Upsilon^\mathbf{l}$ to evaluate to the transaction's accrued log items, both to be formally defined later.

\subsection{Substate}
Throughout transaction execution, we accrue certain information that is acted upon immediately following the transaction. We call this \textit{transaction substate}, and represent it as $A$, which is a tuple:
\begin{equation}
A \equiv (A_\mathbf{s}, A_\mathbf{l}, A_r)
\end{equation}

>>>>

\begin{enumerate}
\item La transazione è un RLP ben strutturata, con nessun ulteriore byte;
\item la firma della transazione è valida;
\item il nonce della transazione è valido (equivalnte al nonce attuale dell'account del mittente);
\item il limite del gas non è inferiore al gas intrinseco, $g_0$, impiegato dalla transazione;
\item il saldo dell'account del mittente contiene almeno il costo, $v_0$, richiesto dal pagamento anticipato.
\end{enumerate}

Formalmente, consideriamo la funzione $\Upsilon$, con $T$ che è una transazione e $\boldsymbol{\sigma}$ lo stato:
\begin{equation}
\boldsymbol{\sigma}' = \Upsilon(\boldsymbol{\sigma}, T)
\end{equation}

Quindi $\boldsymbol{\sigma}'$ è lo stato successivo alla transazione. Definiamo anche $\Upsilon^g$ per valutare l'ammontare di gas usato nell'esecuzione di una transazione e $\Upsilon^\mathbf{l}$ per stimare gli oggetti accumalati nel log della transazione, entrambi definiti successivamente.

\subsection{Substate}
Attraverso l'escuzione della transazione, we accrue certain information that is acted upon immediately following the transaction. We call this \textit{transaction substate}, and represent it as $A$, which is a tuple:
\begin{equation}
A \equiv (A_\mathbf{s}, A_\mathbf{l}, A_r)
\end{equation}
